---
title: "Main and sensitivity analyses"
author: "Kate Tran"
date: "2022-11-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(lme4)
library(sjPlot)

source("../utility_fun.R")
```

# Read the data
```{r}
# 21 SITES
climate_data <- readRDS("../data/dataset_14d_4to10_21sites.rds")
# In the sensitivity analysis
climate_data_sens <- readRDS("../data/dataset_14d_5to9_21sites.rds")
climate_data_beforeCovid <- climate_data %>% filter(year_14d < 2020)
## 11 SITES
climate_data_11sites <- readRDS("../data/dataset_14d_4to10_11sites.rds")

```

# Define variables/covariates
```{r}

random_effect <- c("(1 | site_id_l_br/rel_family_id/src_subject_id)")
race <- c("race_black", "race_white", "ethnicity_hisp")
var_covariates_1 <- c("scale(interview_age)", "scale(interview_age)^2", "scale(interview_age)^3", "sex_br", "scale(household_income)")
var_covariates_2 <- c(var_covariates_1, "scale(reshist_addr1_d1a)", "scale(reshist_addr1_walkindex)", "scale(reshist_addr1_popdensity)", "scale(reshist_addr1_coi_he_green)")
```


correlation
```{r}
# corr_data = climate_data[, c("interview_age", "sex_br", "household_income", "race_black", "race_white", "ethnicity_hisp", "reshist_addr1_d1a", "reshist_addr1_walkindex", "reshist_addr1_popdensity", "SA_y", "ksads_externalizing_exclude_attentation_symptoms_sum", "dx90")]
# colnames(corr_data)[11] = "externalizing_exclude_attentation_symptoms"
# 
# cor = qgraph::cor_auto(corr_data)
# testRes = corrplot::cor.mtest(corr_data, conf.level = 0.95)
# 
# png("../plots/correlation.png", width = 1000, height = 1000)
# corrplot::corrplot(cor, method = 'color', type = 'upper',
#                    p.mat = testRes$p, sig.level = c(0.001, 0.01, 0.05),
#                    number.cex=0.70, insig = 'label_sig',
#                    tl.col = "black", tl.srt = 45,
#                    diag = FALSE,
#                    pch.col = 'grey20', order = 'original', 
#                    pch.cex = 0.7, tl.cex = 0.7, cl.cex = 0.7, cl.ratio = 0.4)

```

# Analysis
## Main analysis: combined past/current externalizing symptoms (ksads_externalizing_exclude_attentation_symptoms_sum)
```{r}
mod_ksads_0 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", 
                                predictor = "scale(dx90)", 
                                variables = random_effect, var_added = NULL), 
                     data = climate_data,
                     family = poisson,
                     control=glmerControl(check.nobs.vs.nlev = "ignore",
                                          check.nobs.vs.rankZ = "ignore",
                                          check.nobs.vs.nRE="ignore",
                                          optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_1 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", 
                                predictor = "scale(dx90)", 
                                variables = random_effect, var_added = var_covariates_1), 
                     data = climate_data, 
                     family = poisson,
                     control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_2 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", 
                                predictor = "scale(dx90)", 
                                variables = random_effect, var_added = var_covariates_2), 
                     data = climate_data, 
                     family = poisson,
                     control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))


# Table 2
tab_model(mod_ksads_0, mod_ksads_1, mod_ksads_2, file= "../outputs/main_results.xls")
```


## Main analysis: outcome lifetime suicide attempt (SA_y)
```{r}
# Table 3
mod_SA_0 <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, var_added = NULL), 
                  data = climate_data, family = binomial, nAGQ = 0)

mod_SA_1 <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, var_added = var_covariates_1), 
                  data = climate_data, family = binomial, nAGQ = 0)

mod_SA_2 <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, var_added = var_covariates_2), 
                  data = climate_data, family = binomial, nAGQ = 0)

tab_model(mod_SA_0, mod_SA_1, mod_SA_2, file= "../outputs/main_results_sa.xls")
```


## Sensitivity analysis: before Covid
```{r}
mod_beforeCovid_ksads_0 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                       variables = random_effect, var_added = NULL), 
                                 data = climate_data_beforeCovid, 
                                 family = poisson,
                                control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                    check.nobs.vs.rankZ = "ignore",
                                                    check.nobs.vs.nRE="ignore",
                                                    optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_beforeCovid_ksads_1 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                       variables = random_effect, var_added = var_covariates_1), data = climate_data_beforeCovid, family = poisson,
                                control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                    check.nobs.vs.rankZ = "ignore",
                                                    check.nobs.vs.nRE="ignore",
                                                    optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_beforeCovid_ksads_2 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                       variables = random_effect, var_added = var_covariates_2), data = climate_data_beforeCovid, family = poisson,
                                control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                    check.nobs.vs.rankZ = "ignore",
                                                    check.nobs.vs.nRE="ignore",
                                                    optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

# Table S10
tab_model(mod_beforeCovid_ksads_0, mod_beforeCovid_ksads_1, mod_beforeCovid_ksads_2, file = "../outputs/before_covid_poisson_ST10.xls")
```

## Sensitivity analysis: May to Sep data
```{r}
mod_MaySep_ksads_0 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                  variables = random_effect, var_added = NULL), data = climate_data_sens, family = poisson,
                           control=glmerControl(check.nobs.vs.nlev = "ignore",
                                               check.nobs.vs.rankZ = "ignore",
                                               check.nobs.vs.nRE="ignore",
                                               optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_MaySep_ksads_1 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                  variables = random_effect, var_added = var_covariates_1), data = climate_data_sens, family = poisson,
                           control=glmerControl(check.nobs.vs.nlev = "ignore",
                                               check.nobs.vs.rankZ = "ignore",
                                               check.nobs.vs.nRE="ignore",
                                               optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_MaySep_ksads_2 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                  variables = random_effect, var_added = var_covariates_2), data = climate_data_sens, family = poisson,
                           control=glmerControl(check.nobs.vs.nlev = "ignore",
                                               check.nobs.vs.rankZ = "ignore",
                                               check.nobs.vs.nRE="ignore",
                                               optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))


# Table S11
tab_model(mod_MaySep_ksads_0, mod_MaySep_ksads_1, mod_MaySep_ksads_2, file = "../outputs/May_to_september_poisson_ST11.xls")
```

## Sensitivity analysis: outcome Present Ksad externalizing symptoms
```{r}
mod_ksads_current_0 <- glmer(get_models(outcome = "ksads_present_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                   variables = random_effect, var_added = NULL), data = climate_data, family = poisson,
                            control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                check.nobs.vs.rankZ = "ignore",
                                                check.nobs.vs.nRE="ignore",
                                                optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_current_1 <- glmer(get_models(outcome = "ksads_present_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                   variables = random_effect, var_added = var_covariates_1), data = climate_data, family = poisson,
                            control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                check.nobs.vs.rankZ = "ignore",
                                                check.nobs.vs.nRE="ignore",
                                                optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_current_2 <- glmer(get_models(outcome = "ksads_present_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                                   variables = random_effect, var_added = var_covariates_1), data = climate_data, family = poisson,
                            control=glmerControl(check.nobs.vs.nlev = "ignore",
                                                check.nobs.vs.rankZ = "ignore",
                                                check.nobs.vs.nRE="ignore",
                                                optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

# Table S12
tab_model(mod_ksads_current_0, mod_ksads_current_1, mod_ksads_current_2, file = "../outputs/Present_Ksad_ST12.xls")
```

## Sensitivity analysis: outcome SA_current_y
```{r}
mod_SA_current_0 <- glmer(get_models(outcome = "SA_current_y", predictor = "scale(dx90)", variables = random_effect, var_added = NULL), 
                          data = climate_data, family = binomial, nAGQ = 0)

mod_SA_current_1 <- glmer(get_models(outcome = "SA_current_y", predictor = "scale(dx90)", variables = random_effect, var_added = var_covariates_1),
                          data = climate_data, family = binomial, nAGQ = 0)

mod_SA_current_2 <- glmer(get_models(outcome = "SA_current_y", predictor = "scale(dx90)", variables = random_effect, var_added = var_covariates_2),
                          data = climate_data, family = binomial, nAGQ = 0)

# Table S13
tab_model(mod_SA_current_0, mod_SA_current_1, mod_SA_current_2, file = "../outputs/sa_current_ST13.xls")
```

## Sensitivity analysis: data of 11 sites (Apr-Oct)
```{r}
mod_ksads_11s_0 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = NULL), data = climate_data_11sites, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_11s_1 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = var_covariates_1), data = climate_data_11sites, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_11s_2 <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = var_covariates_2), data = climate_data_11sites, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

# Table S14
tab_model(mod_ksads_11s_0, mod_ksads_11s_1, mod_ksads_11s_2, file = "../outputs/11_sites_ST14.xls")
```

## Sensitivity analysis: 2 main models  - interaction with race_Black and ethnicity_hisp
```{r}
# Table S9
# externalizing

mod_ksads_0_int <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = c(var_covariates_1, race)), data = climate_data, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_1_int <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = c(var_covariates_1, race, "scale(dx90)*race_black")), data = climate_data, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

mod_ksads_2_int <- glmer(get_models(outcome = "ksads_externalizing_exclude_attentation_symptoms_sum", predictor = "scale(dx90)", 
                           variables = random_effect, var_added = c(var_covariates_1, race, "scale(dx90)*ethnicity_hisp")), data = climate_data, family = poisson,
                    control=glmerControl(check.nobs.vs.nlev = "ignore",
                                        check.nobs.vs.rankZ = "ignore",
                                        check.nobs.vs.nRE="ignore",
                                        optimizer = "bobyqa", optCtrl = list(maxfun = 2e5)))

tab_model(mod_ksads_0_int, mod_ksads_1_int, mod_ksads_2_int, file = "../outputs/ksads_race_interaction_ST9.xls")


# suicide
mod_SA_0_int <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, 
                                 var_added = c(var_covariates_1, race)), 
                  data = climate_data, family = binomial, nAGQ = 0)

mod_SA_1_int <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, 
                                 var_added = c(var_covariates_1, race, "scale(dx90)*race_black")), 
                  data = climate_data, family = binomial, nAGQ = 0)

mod_SA_2_int <- glmer(get_models(outcome = "SA_y", predictor = "scale(dx90)", variables = random_effect, 
                                 var_added = c(var_covariates_1, race, "scale(dx90)*ethnicity_hisp")), 
                  data = climate_data, family = binomial, nAGQ = 0)

tab_model(mod_SA_0_int, mod_SA_1_int, mod_SA_2_int, file = "../outputs/SA_race_interaction_ST9.xls")
```













